Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-05-01 01-intro.Rmd
bug fixes/typos

Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D. whose research will be a focal point of this manuscript. The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this manuscript is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking). In it, they outline a framework to estimate *characteristics* of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature. They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated... In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors." The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.

>>>>

Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D. whose research will be a focal point of this manuscript. The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this manuscript is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking). In it, they outline a framework to shrink a *characteristic* of a precision matrix - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature. They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated... In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors." The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
